Current State of Knowledge Representation Systems for Robotics

### 2011-11-22 paper.tex
Reorganized the 'Comparison criteria' section in subsections and paragraphs

\section{Introduction}
\label{sect|intro}

@@

\section{Comparison criteria}
\label{sect|comparison-criteria}

@@

\begin{itemize}
	\item  Expressiveness
	\begin{itemize}
		\item  Which logic formalism (DL, 2nd order\ldots{})
		\item  OWA/CWA
		\item  Representation of uncertainty
		\item  (non) monotonic reasoning
		\item  General knowledge + exception to this knowledge (blue sky/white sky)
		\item  Microtheories
		\item  Lazy evaluation
		\item  Presupposition accomodation (ability to represent facts that are only verbally hinted, but not grounded into perception)
	\end{itemize}

	\item  Explicit modeling of context of knowledge / domain of validity
	\item  Representation of change (\emph{"The pancake dough disappears into a pancake"})
	\item  Support for learning
	\item  Support for introspection?
	\item  Support for prediction/projection?
\end{itemize}

@@

\begin{itemize}
	\item  Knowledge acquisition possible\ldots{}
	\begin{itemize}
		\item  \ldots{}through interaction? How?
		\item  \ldots{}through the Web? How?
		\item  \ldots{}through learning? How?
		\item  \ldots{}through perception? How?
	\end{itemize}
	\item Grounding/anchoring strategies
	\item Ability to automatically create new object instances
	\item Ability to merge modalities
\end{itemize}

\subsection{Integration in a larger robotic architecture}

\begin{itemize}

	\item  Integration with executive layers
	\begin{itemize}
		\item  Events
		\item  Relation to task planning
	\end{itemize}

	\item Interaction with humans

@@

	\item  Scalability and responsiveness
\end{itemize}

@@

\section{Surveyed systems}

@@

\subsection{Anchoring strategies}
\label{sect|peis-anchoring}

@@

\section{Conclusion}
\label{sect|conclusion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sect|intro}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison criteria}
\label{sect|comparison-criteria}

@@

\subsubsection{Expressiveness}
\label{sect|expressiveness}

\paragraph{Logics formalism}

Which logic formalism (DL, 2nd order\ldots{})

\paragraph{Open World Assumption or Close World Assumption}

\paragraph{(non) monotonic reasoning}

\paragraph{General knowledge + exception to this knowledge (blue sky/white sky)}

\paragraph{Representation of uncertainty}

\paragraph{Representation of time}

\paragraph{Representation of change}

E.g. \emph{"The pancake dough disappears into a pancake"}

\paragraph{Context and Microtheories}
Explicit modeling of context of knowledge / domain of validity

\subsubsection{Presupposition accomodation}
\label{sect|presupposition-accomodation}

\emph{Presupposition accomodation} is the ability to acquire and represent facts that are not
grounded into perception. A typical example is a human telling the robot that
\emph{"there is big blue sphere behind you!"}.

\subsubsection{Lazy evaluation}
\label{sect|lazy-evaluation}

\subsubsection{Introspection}
\label{sect|introspection}
Support for introspection?

\subsubsection{Prediction and projection tasks}
\label{sect|prediction-projection}

Levesque~\cite{Levesque2007} distinguish two main tasks, the \emph{projection task} and the \emph{legality task}.

\paragraph{Projection task}: determining whether or not some condition while hold after a sequence of actions.

\paragraph{Legality task}: determining whether a sequence of action can be performed starting in some initial state.

\subsubsection{Learning}
\label{sect|learning}

@@

\subsubsection{Knowledge acquisition}
\label{sect|knowledge-acquisition}

\paragraph{Perception}
\paragraph{Interaction}
\paragraph{External sources (Web, upper ontologies, ...)}
\paragraph{Learning}

\subsubsection{Grounding/anchoring strategies}
\label{sect|grounding}

\subsubsection{Ability to automatically create new object instances}
\label{sect|new-instances}

\subsubsection{Ability to merge modalities}
\label{sect|modalities-merging}

\subsection{Integration in a larger robotic architecture}
\label{sect|integration-robot}

\subsubsection{Integration with executive layers}
\label{sect|integration-executive-layers}

\paragraph{Events}

\paragraph{Relation to task planning}

\subsubsection{Interaction with humans}
\label{sect|hri}

@@

\subsubsection{Scalability and responsiveness}
\label{sect|scalability}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Surveyed systems}

@@

\subsubsection{Anchoring strategies}
\label{sect|peis-anchoring}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sect|conclusion}
